Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-11 paper.tex
update

\institute{Middlesex University London and\\ Technische Universit\"at Berlin\\
\email{f.kammueller@mdx.ac.uk|bianca.lutz@campus.tu-berlin.de}
}
\maketitle
\begin{abstract}
We provide a model in the Isabelle Infrastructure framework of the recently published German
Corona-virus warning app. The app supports breaking infection chains by informing users
whether they have been in close contact to an infected person. The app has a decentralized
architecture that supports anonymity of users.
We provide a formal model of the existing app with the Isabelle Infrastructure framework
to show up some natural attacks in a very abstract model. We then use the security
refinement process of the Isabelle Infrastructure framework to highlight how the use of
continuously changing ephemeral ids improves the anonymity.
\end{abstract}

\section{Introduction}
\label{sec:intro}
The German Chancellor Angela Merkel has strongly supported the publication of
the mobile phone Corona-virus warning app (CWA; \cite{cwa:github}) by publicly proclaiming that the ``Corona
App deserves your trust'' \cite{bundes:20}. Many millions of mobile phone users
in Germany have downloaded the app with 6 million on the first day.
CWA is one amongst many similar applications that aim at the very important goal
to ``break infection chains'' by providing timely information to users of whether they
have been in close proximity to a person who tested positive for COVID-19.

%The CWA
%has taken a long time to develop being published only on
%16th June 2020. It
%was a quite costly project but this was mainly due to the management of
%Telekom and SAP being in the driving seat. But the app has been designed with great
The app was designed with great
attention on privacy: a distributed architecture \cite{cwa:arch} has been adopted %after a long and
%heated debate with supporters of a central architecture. The distributed architecture is
that is
based on a very clever application design whereby clients broadcast
highly anonymized so called ``Ephemeral Ids'' via Bluetooth and
store those ids of people in close proximity.
%highly anonymized so called ``Ephemeral IDs'' at physical locations via the
%Bluetooth Low Energy Beacon protocol.
%The app saves those ids of people in close proximity.
Infected persons report their infection by uploading their ids to a central server, providing all clients the means to assess exposure risk locally,
hence, stored contact data has never to be shared.
%Infected persons report their infection to a central server,
%which, in turn, provides all clients the means to reconstruct the ids
%used by reported cases over the last 14 days.
%
%When at a later date an infected person reports his infection to a central server,
%all clients are provided the means to reconstruct the ids used by this particular
%person's device over the last 14 days.
%Therefore, exposure risks can be evaluated locally and stored contact data has never to be shared.
%
%, the unique root ID is published
%and in the daily check all mobile phones connecting to the central server download
%the root IDs of infected people. Since the Ephemeral IDs can be mapped to the root ID
%all Ephemeral IDs that have been saved over the last 14 days allow users' phones to
%regularly check whether their user has been exposed to an infected person and issue
%a warning to the user and recommendation to contact health authorities.
%The warning issued by the Corona warning app entitles to
%having a Corona test done (which at the time of writing is not normally possible).

@@

The contributions of this paper are (a) formal re-engineering of the CWA
(b) providing an additional security and privacy analysis with interactive theorem proving
certification of a novel view on the system architecture including actors, locations, and policies,
(c) a formal definition of a security refinement process that allows to improve a system
based on attacks found by the attack tree analysis and (d) an application of the refinement to
improve security of the Corona-virus app specification.

>>>>

\institute{Middlesex University London and\\ Technische Universit\"at Berlin\\
\email{f.kammueller@mdx.ac.uk|bianca.lutz@campus.tu-berlin.de}
}
\maketitle
\begin{abstract}
We provide a model in the Isabelle Infrastructure framework of the recently published German
Corona-virus warning app (CWA). The app supports breaking infection chains by informing users
whether they have been in close contact to an infected person. The app has a decentralized
architecture that supports anonymity of users.
We provide a formal model of the existing app with the Isabelle Infrastructure framework
to show up some natural attacks in a very abstract model. We then use the security
refinement process of the Isabelle Infrastructure framework to highlight how the use of
continuously changing Ephemeral Ids (EphIDs) improves the anonymity.
\end{abstract}

\section{Introduction}
\label{sec:intro}
The German Chancellor Angela Merkel has strongly supported the publication of
the mobile phone Corona-virus warning app (CWA; \cite{cwa:github}) by publicly proclaiming that
``this App deserves your trust'' \cite{bundes:20}. Many millions of mobile phone users
in Germany have downloaded the app with 6 million on the first day.
CWA is one amongst many similar applications that aim at the very important goal
to ``break infection chains'' by providing timely information to users of whether they
have been in close proximity to a person who tested positive for COVID-19.

%The CWA
%has taken a long time to develop being published only on
%16th June 2020. It
%was a quite costly project but this was mainly due to the management of
%Telekom and SAP being in the driving seat. But the app has been designed with great
The app was designed with great
attention on privacy: a distributed architecture \cite{cwa:arch} has been adopted %after a long and
%heated debate with supporters of a central architecture. The distributed architecture is
that is
based on a very clever application design whereby clients broadcast
highly anonymized identifiers (ids)
%so called ``Ephemeral Ids''
via Bluetooth and store those ids of people in close proximity.
%highly anonymized so called ``Ephemeral IDs'' at physical locations via the
%Bluetooth Low Energy Beacon protocol.
%The app saves those ids of people in close proximity.
Infected persons report their infection by uploading their ids to a central server, providing all clients the means to assess exposure risk locally,
hence, stored contact data has never to be shared.
%Infected persons report their infection to a central server,
%which, in turn, provides all clients the means to reconstruct the ids
%used by reported cases over the last 14 days.
%
%When at a later date an infected person reports his infection to a central server,
%all clients are provided the means to reconstruct the ids used by this particular
%person's device over the last 14 days.
%Therefore, exposure risks can be evaluated locally and stored contact data has never to be shared.
%
%, the unique root ID is published
%and in the daily check all mobile phones connecting to the central server download
%the root IDs of infected people. Since the Ephemeral IDs can be mapped to the root ID
%all Ephemeral IDs that have been saved over the last 14 days allow users' phones to
%regularly check whether their user has been exposed to an infected person and issue
%a warning to the user and recommendation to contact health authorities.
%The warning issued by the Corona warning app entitles to
%having a Corona test done (which at the time of writing is not normally possible).

@@

The contributions of this paper are (a) formal re-engineering of the CWA
(b) providing an additional security and privacy analysis with interactive theorem proving
certification of a novel view on the system architecture including actors, locations, and policies,
(c) a formal definition of a security refinement process that allows to improve a system
based on attacks found by the attack tree analysis and (d) an application of the refinement to
improve security of the CWA specification.
